---
title: "Supplement: Helper functions for the muscle testing project"
author: "Joachim Vandekerckhove, Beth Baribault, and Jennifer Wilson"
date: "April 11, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r muscle-testing, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('muscle-testing-helpers.R')
```
A collection of helper functions for the muscle testing paper.

### Function: kendalls.tau()
Computes an unnormalized Kendall's tau-a coefficient
```{r}
kendalls.tau
```

### Function: expected.tau()
Computes tau for every possible outcome and tabulates the frequencies
```{r}
expected.tau
```

### Function: tau.matrix()
Compute probability function for each possible level of concordance
```{r}
tau.matrix
```

### Function: norm()
A normalization function
```{r}
norm
```

### Function: read.mt.data()
This function will read the .csv data file from OSF and format it into a list
```{r}
read.mt.data
```

### Function: process.data()
Extract the relevant subset of the muscle testing data
```{r}
process.data
```

### Function: run.mt()
This function runs the analysis
```{r}
run.mt
```
